---
title: "Excercise 2"
author: "Your name"
date: "27 October 2015"
output: html_document
---

# Rmarkdown
## Excercise 2
### Basic code chunks

This is a very simple paste statement
```{r}
paste("hello world")
```

Notice how the code and the output always shows. To hide the code, set `echo` to `FALSE` like this:

```{r, echo=FALSE}
paste("hello world")
```

If you don't want the chunk to be run at all you can set `eval` to `FALSE`

```{r, eval=FALSE, echo=TRUE}
paste("hello world")
```


You can also insert code in-line. For example, 5 + 9 = `r 5 + 9`, or I think `r paste("EMBL")` is awesome.

### Tables

Here is a simple table

```{r}
# Define a data frame
df = data.frame(number=1:3, letter=c("a", "b", "c"))

# Print my table
print(df)

# Pretty version, you can give it a caption and left-align it with "l"
knitr::kable(df, caption="My table", align="l")
```


### Plots

Here is a simple scatter plot
```{r}
plot(1:10, main="My scatterplot")
```

Here are two plots side-by-side
```{r}
# Create plotting region with one row, two columns
par(mfrow=c(1,2))

# First plot
plot(1:10, main="My scatterplot")

# Second plot
hist(rnorm(100))
```


